Are environmental and geographic variables effective surrogates for genetic variation in conservation planning?

### 2016-04-13 code/rmarkdown/article.Rmd
+ updates to directory structure + use structure for analysis

```{r, include=FALSE}
# set wd
setwd('..')

# load .rda file
try(session::restore.session('results/results.rda'))

@@

## Introduction
<!--  main text -->
The act of setting aside areas for preservation is one of the hallmarks of modern conservation [@r440]. Protected area networks buffer species from anthropogenic impacts and provide places for populations of species to persist. Intra-specific genetic variation is an important component of species persistence, and there has been increasing interest in understanding how to design protected area networks that preserve this variation [@r67; @r3; @r61]. Broadly speaking, genetic variation can be classified as either adaptive or neutral [reviewed in @r48]. Adaptive genetic variation is associated with loci that affect fitness. By preserving existing patterns of adaptive variation, protected areas can ensure that populations with particularly beneficial adaptations are not lost [@r3]. In contrast, neutral genetic variation is associated with loci that do not affect fitness. Neutral variation often reflects the evolutionary history of different populations. By preserving existing patterns of neutral variation, protected areas can secure different genetic lineages and avoid the adverse effects of low genetic diversity [eg. inbreeding depression; @r67]. However, genetic data requires considerable investment to obtain and analyze. As a consequence, conservation planners do not typically use genetic data to inform prioritizations [@r61]. Thus prioritizations may fail to capture species' intra-specific genetic variation, and ultimately fail to deliver long-term conservation outcomes.

>>>>

```{r, include=FALSE}
# set wd
setwd('..')
setwd('..')

# load .rda file
try(session::restore.session('data/results/results.rda'))

@@

## Introduction
<!--  main text -->
The act of setting aside areas for preservation spearheads modern conservation efforts [@r440]. Protected area networks buffer species from anthropogenic impacts and provide places for populations of species to persist. Intra-specific genetic variation underpins species persistence, and there has been increasing interest in understanding how to design protected area networks in a way that maximizes this variation [@r67; @r3; @r61]. Broadly speaking, genetic variation can be classified as either adaptive or neutral [reviewed in @r48]. Adaptive genetic variation is associated with loci that affect fitness. By preserving existing patterns of adaptive variation, protected areas can ensure that populations with particularly beneficial adaptations are not lost [@r3]. In contrast, neutral genetic variation is associated with loci that do not affect fitness. Neutral variation often reflects the evolutionary history of different populations. By preserving existing patterns of neutral variation, protected areas can secure different genetic lineages and avoid the adverse effects of low genetic diversity [eg. inbreeding depression; @r67]. However, genetic data requires considerable investment to obtain and analyze. As a consequence, conservation planners do not typically use genetic data to inform prioritizations [@r61]. Thus prioritizations may fail to capture species' intra-specific genetic variation, and ultimately fail to deliver long-term conservation outcomes.

### 2016-04-13 code/rmarkdown/figures.Rmd
+ updates to directory structure + use structure for analysis

```{r, include=FALSE}
# set wd
setwd('..')

# load .rda file
try(session::restore.session('results/results.rda'))

# set options
options(error=NULL)
```

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```

@@

```{r, echo=FALSE, message=FALSE, fig.width=6, fig.height=4.5, fig.cap='The relationship between surrogates and genetic variation secured in prioritizations. White boxplots show the proportion of genetic variation secured by prioritizations generated using surrogate-based targets. Grey boxplots show the proportion of genetic variation secured by randomly generated prioritizations with the same number of planning units as the surrogate-based prioritizations. Panel (a) shows the relationship between environmental surrogate targets used to generate a prioritization and the proportion of adaptive genetic variation it secures. Similarly, panel (b) shows that for geographic surrogate targets and neutral genetic variation. Box-plots show inter-specific variation in the proportion of genetic variation secured using different surrogate-based targets.'}
# prepare data
correlation.PDF <- correlation.DF %>%
	group_by(Type, Surrogate.target, Method, Species) %>% 
	summarize(genetic.held=mean(genetic.held, na.rm=TRUE)) %>%
	data.frame()

@@

```{r, results='hide', echo=FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=5, fig.cap='The effectiveness of prioritizations at securing genetic variation. The top row of panels (a--b) show the performance of single-species prioritizations generated assuming equal costs among planning costs. The middle row of panels (c--d) show the performance of multi-species prioritizations generated assuming equal costs among planning units. The bottom row of panels (e--f) show the performance of multi-species prioritizations generated using opportunity costs. The left column of panels (a, c, d) and the right column of panels (b, d, f) show the proportion of adaptive and neutral genetic variation secured (respectively). Box plots show the effectiveness of prioritizations generated using amount-based targets, amount-based and surrogate-based targets, and amount-based and genetic-based targets for each species. Letters denote significant differences ($P < 0.05$).'}
# prepare data for plotting
scenario.PDF <- scenario.DF %>% group_by(Prioritisation, Context, Metric) %>% 
	mutate(
		letter.height=max(genetic.held, na.rm=TRUE)+0.1,
		Combination=paste0(Prioritisation,'.',Metric,'.',Context)) %>%
	filter(c(TRUE, rep(FALSE, length(Context)-1))) %>% 
	ungroup() %>%
	group_by(Context, Metric) %>% 
	mutate(
		panel.letter=paste0(
			'(',letters[(as.integer(Context)*2)-1 + (as.integer(Metric)-1)],')'
		),
		panel.letter=c(as.character(panel.letter[1]), rep(NA_character_, length(Context)-1))
	) %>% 
	ungroup() %>% 
	left_join(
		data.frame(
			letter=unname(scenario.G.cld$Letters),
			Combination=as.character(names(scenario.G.cld$Letters))
		) %>% mutate(Combination=as.character(Combination)),
		by='Combination'
	) %>% data.frame()

>>>>

```{r, include=FALSE}
# set wd
setwd('..')
setwd('..')

# load .rda file
try(session::restore.session('data/results/results.rda'))

# set options
options(error=NULL)

@@

```{r, echo=FALSE, message=FALSE, fig.width=6, fig.height=4.5, fig.cap='The relationship between surrogates and genetic variation secured in prioritizations. White boxplots show the proportion of genetic variation secured by prioritizations generated using surrogate-based targets. Grey boxplots show the proportion of genetic variation secured by randomly generated prioritizations with the same number of planning units as the surrogate-based prioritizations. Panel (a) shows the relationship between environmental surrogate targets used to generate a prioritization and the proportion of adaptive genetic variation it secures. Similarly, panel (b) shows that for geographic surrogate targets and neutral genetic variation. Box-plots show inter-specific variation in the proportion of genetic variation secured using different surrogate-based targets.'}
# prepare data
correlation.PDF <- correlation.sub.DF %>%
	group_by(Type, Surrogate.target, Method, Species) %>% 
	summarize(genetic.held=mean(genetic.held, na.rm=TRUE)) %>%
	data.frame()

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width=5, fig.height=5, fig.cap='The effectiveness of prioritizations at securing genetic variation. The top row of panels (a--b) show the performance of single-species prioritizations generated assuming equal costs among planning costs. The middle row of panels (c--d) show the performance of multi-species prioritizations generated assuming equal costs among planning units. The bottom row of panels (e--f) show the performance of multi-species prioritizations generated using opportunity costs. The left column of panels (a, c, d) and the right column of panels (b, d, f) show the proportion of adaptive and neutral genetic variation secured (respectively). Box plots show the effectiveness of prioritizations generated using amount-based targets, amount-based and surrogate-based targets, and amount-based and genetic-based targets for each species. Letters denote significant differences ($P < 0.05$).'}
# prepare data for plotting
scenario.PDF <- scenario.DF %>% group_by(Prioritisation, Context, Metric) %>% 
	mutate(
		letter.height=max(genetic.held, na.rm=TRUE)+0.1,
		Combination=paste0(Prioritisation,'.',Metric,'.',Context)) %>%
	filter(c(TRUE, rep(FALSE, length(Context)-1))) %>% 
	ungroup() %>%
	group_by(Context, Metric) %>% 
	mutate(
		panel.letter=paste0(
			'(',letters[(as.integer(Context)*2)-1 + (as.integer(Metric)-1)],')'
		),
		panel.letter=c(as.character(panel.letter[1]), rep(NA_character_, length(Context)-1))
	) %>% 
	ungroup() %>% 
	left_join(
		data.frame(
			letter=unname(scenario.G.cld$Letters),
			Combination=as.character(names(scenario.G.cld$Letters))
		) %>% mutate(Combination=as.character(Combination)),
		by='Combination'
	) %>% data.frame()
